Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-05 tese2/abstract.tex
reviewed abstract

\ac{WebRTC} technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follow the hypermedia concept, which makes \ac{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
{\color{blue}The web browser platform provides an abstraction layer that makes possible to create applications that run indenpendently from the operating system.}
The native support of \ac{WebRTC} in operating systems extends its usage to outside the web browser, allowing to explore functionalities that web browsers are poor to support such as video recording and massive information storage.

@@

@@

>>>>

\ac{WebRTC} technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follows the hypermedia concept, which makes \ac{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
{\color{blue}The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.}
The native support for \ac{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

@@

%RP acho que estás a vender muito mal o teu trabalho. O abstract é a primeira caisa que se lê e em função disso decidimos se lemos mais ou não. Tens aqui a oportunidade de chamar a atenção para algumas das funções inovadoras. O texto está muit genérico. podes falar em coisas concretas: video conferência, chat, edição colaborativo de documento, partilha de ficheiros, possibilidade de criar legendas, tags, etc. Possibilidade de navegar, voltar atrás, etc como no IPTV. Gestão de amigos, gerir salas, etc, etc.

@@

%RP em vez de ``provide the results for its implementation and evaluation'', diz algo como: ``this work was evaluated using a panel of 20 users, who reported that they liked to use it and thought it to be extremelly inovative ... and if given the change, would use it ...''
